Robertson and Cao Project

### 2024-04-04 products/manuscript/Manuscript.qmd
Demographics table and lasso
Demographics table was added to the manuscript and the first round of lasso was fitted. However, for some reason the estimate for all of the predictors chosen by LASSO were equal to zero. I am not sure if this is because the penalty is too high or why else. I will try and research this.

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(here)
```

@@

We use our exploratory analysis to determine the distribution of our predictors, including the socioeconomic variables that we chose for analysis.
The overall distribution of each factor variable is shown below.
![Table 1.]
The distribution of the numerical income to poverty ratio can be shown below.
It displays a value from 1-3.
A ratio displaying less than 1 depicts an income less than the poverty level.Any income ratio \>1 indicates an income greater than the poverty level.
Most of the observations were gathered from households with income ratios of 3, as shown by the skewed plot below.

@@

Nest, the distribution of surveys given per state was analyzed.
The state variable shows a more uniformed distribution, suggesting that the observations were gathered fairly across the US states and territory.
Although it is noted a few territories provides 0 observations.
![Figure 2. State distribution](./images/state.distribution.png)

>>>>

```{r setup, include=FALSE}
library(here)
library(knitr)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

@@

We use our exploratory analysis to determine the distribution of our predictors, including the socioeconomic variables that we chose for analysis.
The overall distribution of each factor variable is shown below.

```{r}
#| label: Table1
#| tbl-cap: "Table 1.Socioeconomic characteristics of U.S. teenagers who have completed or are up-to-date with HPV vaccination series."
#| echo: FALSE
Table1 <- readRDS(here("results/tables/table1.rds"))
kable(Table1)
```
```

The distribution of the numerical income to poverty ratio can be shown below.
It displays a value from 1-3.
A ratio displaying less than 1 depicts an income less than the poverty level.Any income ratio \>1 indicates an income greater than the poverty level.
Most of the observations were gathered from households with income ratios of 3, as shown by the skewed plot below.

@@

Next, the distribution of surveys given per state was analyzed.
The state variable shows a more uniformed distribution, suggesting that the observations were gathered fairly across the US states and territory.
Although it is noted a few territories provides 0 observations.
![Figure 2. State distribution](./images/state.distribution.png)
